HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex
ondrej's comments and fixes

\section{UCCA Annotation}
Source sentences are all in English, and the UCCA annotation was performed by four
computational linguists\oa{were there no other annotators from Prague? Ondrej
does not remember! Was it just Ondrej+Jana Sindlerova? Then it would be one
computer scientist and one linguist for Czech.}.

>>>>

\subsection{UCCA Annotation}
Source sentences are all in English, and the UCCA annotation was performed by four
computational linguists\oa{were there no other annotators from Prague? Ondrej
does not remember! Was it just Ondrej+Jana Sindlerova? Then it would be one
computer scientist and one linguist for Czech.}.
